---
title: "p8105_hw2_fs2757"
author: "FEI SUN"
date: "2021/10/5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
```
##  Problem 1
First I read and clean the Mr. Trash Wheel sheet, and I use reasonable variable names for this data. Furthermore, I omit rows that do not include dumpster-specific data and round the number of sports balls to the nearest integer.
```{r}
TrashWheel_data = read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "Mr. Trash Wheel",range = "A2:N408")
TrashWheel_data = 
                  janitor::clean_names(TrashWheel_data) %>% 
                  drop_na(dumpster)%>% 
                  mutate(sports_balls = round(sports_balls,digits = 0))   
skimr::skim(TrashWheel_data)
```
Read and clean precipitation data for 2018 and 2019. For each, omit rows without precipitation data and add a variable for year. Next, combine precipitation datasets and convert month to a character variable (the variable month.name is built into R and should be useful).
```{r}
precipitation_2019 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2019 Precipitation",skip = 1, range = "A2:B14")%>%
  janitor::clean_names()%>%
  mutate(year= "2019")%>%
  drop_na()

precipitation_2018 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2018 Precipitation",skip = 1, range = "A2:B14")%>%
  janitor::clean_names()%>%
  mutate(year= "2018")%>%
  drop_na()

precipitation20182019 = 
  bind_rows(precipitation_2019, precipitation_2018) %>%
  janitor::clean_names()%>%
  mutate(month = month.name[month]) 
```
For dataset `TrashWheel_data`, in the code `r skimr::skim(TrashWheel_data)`, we could know that the summary information about the dataset. There are `r length(TrashWheel_data)` observations, `r nrow(TrashWheel_data)` rows and `r ncol(TrashWheel_data)` columns. By coding `r names(TrashWheel_data)`, we could know that 14 different variable names.

For dataset `precipitation_2019`, in the code `r skimr::skim(precipitation_2019)`, we also could know that the summary information. There are `r length(precipitation_2019)` observations, `r nrow(precipitation_2019)` rows and `r ncol(precipitation_2019)` columns. By coding `r names(precipitation_2019)`, we could know that 3 different variable names.

For dataset `precipitation_2018`, in the code `r skimr::skim(precipitation_2018)`, we also could know that the summary information. There are `r length(precipitation_2018)` observations, `r nrow(precipitation_2018)` rows and `r ncol(precipitation_2018)` columns. By coding `r names(precipitation_2018)`, we could know that 3 different variable names.

For dataset `precipitation20182019`, in the code `r skimr::skim(precipitation20182019)`, we also could know that the summary information. There are `r length(precipitation20182019)` observations, `r nrow(precipitation20182019)` rows and `r ncol(precipitation20182019)` columns. By coding `r names(precipitation20182019)`, we could know that 3 different variable names.

The total precipitation in 2018 is `r sum(pull(precipitation_2018, total))`, and the median number of sports balls in a dumpster in 2019 is `r  median(pull(filter(TrashWheel_data, year == 2019),sports_balls))`.



##  Problem 2

