---
title: "p8105_hw2_fs2757"
author: "FEI SUN"
date: "2021/10/5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
library(dplyr)
```
##  Problem 1
First I read and clean the Mr. Trash Wheel sheet, and I use reasonable variable names for this data. Furthermore, I omit rows that do not include dumpster-specific data and round the number of sports balls to the nearest integer.
```{r}
TrashWheel_data = read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",sheet = "Mr. Trash Wheel",range = "A2:N534")
TrashWheel_data = 
  janitor::clean_names(TrashWheel_data) %>% 
  drop_na(dumpster)%>% 
  mutate(sports_balls = round(sports_balls,digits = 0))   
skimr::skim(TrashWheel_data)
```
Read and clean precipitation data for 2018 and 2019. For each, omit rows without precipitation data and add a variable for year. Next, combine precipitation datasets and convert month to a character variable (the variable month.name is built into R and should be useful).
```{r}
precipitation_2019 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",sheet = "2019 Precipitation",skip = 1, range = "A2:B14")%>%
  janitor::clean_names()%>%
  mutate(year= "2019")%>%
  drop_na()

precipitation_2018 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",sheet = "2018 Precipitation",skip = 1, range = "A2:B14")%>%
  janitor::clean_names()%>%
  mutate(year= "2018")%>%
  drop_na()

precipitation20182019 = 
  bind_rows(precipitation_2019, precipitation_2018) %>%
  janitor::clean_names()%>%
  mutate(month = month.name[month]) 
```
For dataset `TrashWheel_data`, in the code `r skimr::skim(TrashWheel_data)`, we could know that the summary information about the dataset. There are `r length(TrashWheel_data)` observations, `r nrow(TrashWheel_data)` rows and `r ncol(TrashWheel_data)` columns. By coding `r names(TrashWheel_data)`, we could know that 14 different variable names.

For dataset `precipitation_2019`, in the code `r skimr::skim(precipitation_2019)`, we also could know that the summary information. There are `r length(precipitation_2019)` observations, `r nrow(precipitation_2019)` rows and `r ncol(precipitation_2019)` columns. By coding `r names(precipitation_2019)`, we could know that 3 different variable names.

For dataset `precipitation_2018`, in the code `r skimr::skim(precipitation_2018)`, we also could know that the summary information. There are `r length(precipitation_2018)` observations, `r nrow(precipitation_2018)` rows and `r ncol(precipitation_2018)` columns. By coding `r names(precipitation_2018)`, we could know that 3 different variable names.

For dataset `precipitation20182019`, in the code `r skimr::skim(precipitation20182019)`, we also could know that the summary information. There are `r length(precipitation20182019)` observations, `r nrow(precipitation20182019)` rows and `r ncol(precipitation20182019)` columns. By coding `r names(precipitation20182019)`, we could know that 3 different variable names.

The total precipitation in 2018 is `r sum(pull(precipitation_2018, total))`, and the median number of sports balls in a dumpster in 2019 is `r  median(pull(filter(TrashWheel_data, year == 2019),sports_balls))`.

  

##  Problem 2
```{r}
pols_month=read_csv("/Users/sunfei/Desktop/pols-month.csv") %>%
  janitor::clean_names() %>%
  separate(mon,into = c("year","month","day"))%>%
  mutate(month = month.name[as.numeric(month)],day = as.numeric(day),year = as.numeric(year))%>%
  mutate(president = ifelse(prez_dem == 0, "gop", "dem"))%>%
  select(-"day", -"prez_gop", -"prez_dem") 
          
snp=read_csv("/Users/sunfei/Desktop/snp.csv")%>%
  janitor::clean_names()%>%
  mutate(date = lubridate::mdy(date)) %>% 
  separate(date, into = c("year", "month", "day")) %>% 
  mutate(month = month.name[as.numeric(month)],day = as.numeric(day),year = as.numeric(year)) %>% 
  select(-"day") 

unemployment=read_csv("/Users/sunfei/Desktop/unemployment.csv")%>%
  pivot_longer(Jan:Dec, names_to = "month", values_to = "unemployment")%>% 
  janitor::clean_names()%>%
  mutate(year = as.numeric(year))

mergeddata_1=left_join(pols_month, snp, by = c("year", "month")) 
mergeddata_2=left_join(unemployment,mergeddata_1, by = c("year", "month"))
```
The datasets `pols_month` has `r nrow(pols_month)` rows and `r ncol(pols_month)` columns. By coding `r names(pols_month)`, we could know that 9 different variable names. Also I could get the range of years by coding `r range(pull(pols_month, year))`.

The datasets `snp` has `r nrow(snp)` rows and `r ncol(snp)` columns. By coding `r names(snp)`, we could know that 3 different variable names. Also I could get the range of years by coding `r range(pull(snp, year))`.

The datasets `unemployment` has `r nrow(unemployment)` rows and `r ncol(unemployment)` columns. By coding `r names(unemployment)`, we could know that 3 different variable names. Also I could get the range of years by coding `r range(pull(unemployment, year))`.

The datasets `mergeddata_2` has `r nrow(mergeddata_2)` rows and `r ncol(mergeddata_2)` columns. By coding `r names(mergeddata_2)`, we could know that 11 different variable names. Also I could get the range of years by coding `r range(pull(mergeddata_2, year))`.


##  Problem 3
```{r}
# cleaning the data/converting the uppercase letters about name and gender to lowercase string/converting ambiguous ethnicity word to the official one.
PopularBabyNames=read_csv("/Users/sunfei/Desktop/Popular_Baby_Names.csv")%>%
  janitor::clean_names()%>%
  mutate(childs_first_name = tolower(childs_first_name),ethnicity = as.factor(ethnicity),gender = tolower(gender))%>%
  mutate(ethnicity = recode(ethnicity, `ASIAN AND PACI` = "ASIAN AND PACIFIC ISLANDER", `BLACK NON HISP ` = "BLACK NON HISPANIC", `WHITE NON HISP` = "WHITE NON HISPANIC"))

# removing the duplicated rows 
PopularBabyNames = PopularBabyNames[!duplicated(PopularBabyNames),]

# showing and doing a clear and reader-friendly table about the rank in popularity of the name “Olivia” as a female name 
olivia = PopularBabyNames %>% 
  filter(childs_first_name == "olivia") %>% 
  pivot_wider(names_from = "year_of_birth", values_from = "count")
  knitr::kable(olivia)

# showing and doing a clear and reader-friendly table about the rank in popularity of the male name
popularmalename=PopularBabyNames %>% 
  filter(gender == "male", rank == "1") %>% 
  pivot_wider(names_from = "year_of_birth", values_from = "count")
  knitr::kable(popularmalename)

# showing a graph about the name and the rank in popularity of white non-hispanic make children born in 2016
malewhitenonhispanicin2016=PopularBabyNames %>% 
  filter(gender == "male", year_of_birth=="2016",ethnicity=="WHITE NON HISPANIC")  

ggplot(malewhitenonhispanicin2016, aes(x = rank, y = count)) + geom_point()+ylab("number of children with the popularity name") + xlab("rank in popularity name")
```
