---
title: "p8105_hw2_fs2757"
author: "FEI SUN"
date: "2021/10/5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
getwd()
```
##  Problem 1
First I read and clean the Mr. Trash Wheel sheet, and I use reasonable variable names for this data. Furthermore, I omit rows that do not include dumpster-specific data and round the number of sports balls to the nearest integer.
```{r}

TrashWheel_data = read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "Mr. Trash Wheel",range = "A2:N408")
TrashWheel_data = 
                  janitor::clean_names(TrashWheel_data) %>% 
                  drop_na(dumpster)%>% 
                  mutate(sports_balls = round(sports_balls,digits = 0))        
```
Read and clean precipitation data for 2018 and 2019. For each, omit rows without precipitation data and add a variable for year. Next, combine precipitation datasets and convert month to a character variable (the variable month.name is built into R and should be useful).
```{r}
precipitation_2019 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2019 Precipitation",skip = 1)%>%
  janitor::clean_names()%>%
  mutate(year= "2019")%>%
  drop_na()

precipitation_2018 = 
  read_excel("/Users/sunfei/Desktop/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2018 Precipitation",skip = 1)%>%
  janitor::clean_names()%>%
  mutate(year= "2018")%>%
  drop_na()

precip20182019 = 
  bind_rows(precipitation_2019, precipitation_2018) %>%
  mutate(month.name[month]) 
  

```
